On $K_2$-analogue of Serre problem for $\SL_4$

### 2018-10-14 paper.tex
Minor

It is clear the above construction is functorial in $R$, for a ring map $f\colon R\to S$ we denote the corresponding map of Steinberg groups by $f_*$.

%TODO: define Weyl elements w_{\alpha}(\varepsilon)
Recall that for $\alpha\in\Phi$, $\varepsilon\in R^*$ the semisimple root elements $h_\alpha(\varepsilon)$ are defined as $h_\alpha(\varepsilon)=w_\alpha(\varepsilon)w_\alpha(-1)$.
Denote by $\StW(\Phi, R)$ the subgroup of $\St(\Phi, R)$ generated by all elements
$w_\alpha(\varepsilon)$, $\varepsilon\in R^*$, $\alpha\in\Phi$, and by $\StH(\Phi,R)$
 the subgroup generated by all elements $h_\alpha(\varepsilon)$, $\varepsilon\in R^*$, $\alpha\in\Phi$.
We also denote by $\StB(\Phi, R)$ the product of the two subgroups $\StH(\Phi, R)$ and $\UU(\Phi^+, R)$ inside $\St(\Phi, R)$.

@@

\begin{equation}
 \xymatrix{ 1 \ar[r] & C(\Phi, R, I) \ar[r] & \St(\Phi, R, I) \ar[r]^{\ext{I}} & \St(\Phi, R) \ar[r]^{\pi_*} & \St(\Phi, R/I) \ar[r] & 1 }
\end{equation}

@@

\begin{lemma}\label{lem:bruhat}
Let $\Phi$ be any irreducible root system.
Let $\Phi^+$, $\Phi^{+'}$ be two systems of positive roots in $\Phi$.
 \begin{lemlist}
\item  The Steinberg group
$\St(\Phi,A)$ admits the following analogue of the Bruhat decomposition:
\begin{equation}\label{eq:bruhat}
\St(\Phi,A) =\bigsqcup_{w\in W(\Phi)} \left(\UU(\Phi^{+'}, A)\cdot wH(\Phi,A)\cdot\UU(\Phi^+, A) \cdot
\ker\bigl(\St(\Phi,A) \xrightarrow{\pi^*} \St(\Phi,k)\bigr)\right).
\end{equation}
\item Assume that $uwhvl=u'w'h'v'l'$ for some $u,u'\in \UU(\Phi^{+'}, A)$, $w,w'\in W(\Phi)$,
$h,h'\in H(\Phi,A)$, and $l,l'\in \Ker\bigl(\St(\Phi,A) \xrightarrow{\pi^*} \St(\Phi,k)\bigr)$. Then
$w=w'$,
$$
h^{-1}h'\in \Sym(\Phi,A)\cdot\ker\bigl(H(\Phi,A) \xrightarrow{\pi^*} H(\Phi,k)\bigr),
$$
and
there exist $a\in \UU(\Phi^{+'},m)$ such that $w^{-1}(u^{-1}u'a)w\in \UU(\Phi^+,R)$,
and $b\in\UU(\Phi^+,m)$ such that
$$
b=v^{-1}(u^{-1}u')^{wh}v'=l(l')^{-1}.
$$
 \end{lemlist}
\end{lemma}

>>>>

It is clear the above construction is functorial in $R$, for a ring map $f\colon R\to S$ we denote the corresponding map of Steinberg groups by $f^*$.

For $\alpha\in\Phi$ and $\varepsilon \in R^*$ we define the elements $w_\alpha(\varepsilon) = x_\alpha(\varepsilon) x_{-\alpha}(-\varepsilon^{-1}) x_\alpha(\varepsilon)$,
 and $h_\alpha(\varepsilon)=w_\alpha(\varepsilon)w_\alpha(-1)$ (recall that $h_\alpha(\varepsilon)$ are sometimes called {\it semisimple root elements}).
%TODO: Write needed identities for w & h here
\begin{comment} 
 Let us recall the standard identities which hold for these elements.
\begin{lemma} \label{lem:Mat5.2}
 The following identities are true.
 \begin{lemlist}
  \item Lol
  \item Lol2
 \end{lemlist}
\end{lemma}
\end{comment}

Denote by $\StW(\Phi, R)$ the subgroup of $\St(\Phi, R)$ generated by all elements
$w_\alpha(\varepsilon)$, $\varepsilon\in R^*$, $\alpha\in\Phi$, and by $\StH(\Phi,R)$
 the subgroup generated by all elements $h_\alpha(\varepsilon)$, $\varepsilon\in R^*$, $\alpha\in\Phi$.
We also denote by $\StB(\Phi, R)$ the product of the two subgroups $\StH(\Phi, R)$ and $\UU(\Phi^+, R)$ inside $\St(\Phi, R)$.

@@

\begin{equation}
 \xymatrix{ 1 \ar[r] & C(\Phi, R, I) \ar[r] & \St(\Phi, R, I) \ar[r]^{\ext{I}} & \St(\Phi, R) \ar[r]^{\pi^*} & \St(\Phi, R/I) \ar[r] & 1 }
\end{equation}

@@

\begin{lemma}\label{lem:bruhat}
Let $A$ be a local ring with maximal ideal $M$ and let $\Phi^+$ be the subset of positive roots of $\Phi$.
\begin{lemlist}
\item The Steinberg group $\St(\Phi,A)$ admits the following analogue of the Bruhat decomposition:
\begin{equation}\label{eq:bruhat} \St(\Phi,A) =\bigsqcup_{w\in W(\Phi)} \left(\UU(\Phi^{+'}, A)\cdot wH(\Phi,A)\cdot\UU(\Phi^+, A) \cdot
                                  \ker\bigl(\St(\Phi,A) \xrightarrow{\pi^*} \St(\Phi,k)\bigr)\right). \end{equation}
\item Assume that $uwhvl=u'w'h'v'l'$ for some $u,u'\in \UU(\Phi^{+'}, A)$, $w,w'\in W(\Phi)$,
$h,h'\in H(\Phi,A)$, and $l,l'\in \Ker\bigl(\St(\Phi,A) \xrightarrow{\pi^*} \St(\Phi,k)\bigr)$. Then
$w=w'$,
$$ h^{-1}h'\in \Sym(\Phi,A)\cdot\ker\bigl(H(\Phi,A) \xrightarrow{\pi^*} H(\Phi,k)\bigr), $$
and there exist $a\in \UU(\Phi^{+'},m)$ such that $w^{-1}(u^{-1}u'a)w\in \UU(\Phi^+,R)$,
and $b\in\UU(\Phi^+,m)$ such that
$$ b=v^{-1}(u^{-1}u')^{wh}v'=l(l')^{-1}. $$
\end{lemlist}
\end{lemma}
